An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-17 VLDB2026/main.tex
fig

	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains. We independently generate attribute for each dataset.
	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.
	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.

@@

		% 第二行：两张子图，左侧宽度是右侧的两倍
		\begin{subfigure}{0.64\textwidth} % 2/3 宽度
			\centering

			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms optimized for high AS.}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hspace{1mm} % 增加水平间距
		\begin{subfigure}{0.32\textwidth} % 1/3 宽度
			\centering

			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms insensitive to AS.}
			\label{fig:exp_5_2_3}
		\end{subfigure}

>>>>

	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains. We independently generate attribute for each dataset.
	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.

%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.

	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluate the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability. Notably, the previously discussed datasets primarily relied on synthetic attributes for experimentation. Therefore, we additionally incorporated two datasets containing real attributes for a more comprehensive evaluation:}

	YT-Audio-Real dataset: We utilized the URLs provided by the YouTube8M dataset to crawl the corresponding video category IDs and view counts as their real attributes.

@@

		% 第二行：两张子图，左侧宽度是右侧的两倍
		\begin{subfigure}{0.627\textwidth} % 2/3 宽度
			\centering

			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms optimized for high AS.}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hspace{1mm} % 增加水平间距
		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
			\centering

			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms insensitive to AS.}
			\label{fig:exp_5_2_3}
		\end{subfigure}
